A Road Segment Prioritization Approach for Cycling Infrastructure

### 2023-04-24 README.Rmd
add grise+geneidy citation

*OD* data can be obtained from a range of sources,
including GPS data, household travels surveys and census data on work
locations. In areas where observed OD data is unavailable, modelling
techniques such as spatial interaction models can be used to estimate
travel volumes between zones [@black1995spatial; @martinez2013new;
@wilson1971family]. In this paper we use open access data from the UK
census [@ONS2011flowdata], which contains aggregate statistics on
number of commuters between administrative zones --- Middle layer Super
Output Areas (MSOA) --- by mode of travel. MSOAs have an average
population of just over 8000 [@ofn2018population].^[ See
<https://wicid.ukdataservice.ac.uk/> for open access to the OD data.]
Figures \@ref(fig:potdemhistograms) and \@ref(fig:desirefacetcycling)
illustrate the proportion of trips cycled by distance and the
geographic extent of the input OD dataset used in this paper.

@@

The approach is not without limitations. The level of detail is only as
good as the granularity of the available data (in this case relatively
coarse zones). @iacono2010measuring note that such large travel zones
are not ideal for understanding route choice behaviour of cyclists and
pedestrians. They also give rise to an \`ecological fallacy' whereby
average characteristics are assumed to apply to all residents of the
aggregated geographical area, suggesting a need for applying the methods
to more granular OD data (and for governments and other
data-collecting organisations to make OD data more
readily available).
The potential demand calculation is also based on cycling in the traditional sense, and does not consider the 
effect of micro-mobility on reducing topology-related impedance to cycling. Given that we are proposing an approach which can accommodate any cycling uptake functions, this is an acceptable limitation.

>>>>

*OD* data can be obtained from a range of sources,
including GPS data, household travels surveys and census data on work
locations. In areas where observed OD data is unavailable, modelling
techniques such as spatial interaction models can be used to estimate
travel volumes between zones [@black1995spatial; @martinez2013new;
@wilson1971family]. In this paper we use open access data from the UK
census [@ONS2011flowdata], which contains aggregate statistics on
number of commuters between administrative zones --- Middle layer Super
Output Areas (MSOA) --- by mode of travel (this is similar to the approach 
used by @grise2018if). 
MSOAs have an average
population of just over 8000 [@ofn2018population].^[ See
<https://wicid.ukdataservice.ac.uk/> for open access to the OD data.]
Figures \@ref(fig:potdemhistograms) and \@ref(fig:desirefacetcycling)
illustrate the proportion of trips cycled by distance and the
geographic extent of the input OD dataset used in this paper.

@@

The approach is not without limitations. The level of detail is only as
good as the granularity of the available data (in this case relatively
coarse zones). @iacono2010measuring note that such large travel zones
are not ideal for understanding route choice behaviour of cyclists and
pedestrians. They also give rise to an \`ecological fallacy' whereby
average characteristics are assumed to apply to all residents of the
aggregated geographical area, suggesting a need for applying the methods
to more granular OD data (and for governments and other
data-collecting organisations to make OD data more
readily available).
The potential demand calculation is also based on cycling in the traditional sense, and does not consider the 
effect of micro-mobility on reducing topology-related impedance to cycling. Given that we are proposing an approach which can accommodate any cycling uptake functions, this is an acceptable limitation. 
The network prioritization is based strongly on potential cycling demand calculations. While this provides a solid supplementary tool for network planning, it would be more useful as part of a multi-criteria approach that considers on-the ground information from existing cyclists, road geometries, and traffic analysis. @grise2018if propose a multi-criteria approach that includes the first of these points.
